Price of Anarchy for Mean Field Games

### 2018-07-14 PoA.tex
continuing to edit proposition 3

In the following, we intend to simplify the explicit solutions (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) for the social costs in the LQEMFG and LQEMKV problems. First, consider the quantity $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$. Using equation (\ref{eq:eta_bar_MFG}), we have:
\begin{equation*}
\begin{split}
&\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
=& - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T ((2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \right]\\
\end{split}
\end{equation*}
Then by integration by parts:
\begin{equation*}
\begin{split}
= & - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2-\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2-2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t\dot{\bar{x}}^{MFG}_t dt \\
& + \int_0^T ( (2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s)) (\bar{x}^{MFG}_t)^2 dt \Bigg] \\
\end{split}
\end{equation*}
Then using equation (\ref{eq:x_bar_MFG}):
\begin{equation*}
\begin{split}
= & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
&- \int_0^T  (\bar{b}_1 \bar{\eta}^{MFG}_t -(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
\end{split}
\end{equation*}
Finally, we solve:
\begin{equation*}
\begin{split}
\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
&+ \int_0^T  (-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
\end{split}
\end{equation*}
If we denote:
\begin{equation*}
\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},
\end{equation*}
\begin{equation*}
h_{var}: = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T,
\end{equation*}
and use the terminal condition for $\bar{\eta}^{MFG}_T$, then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
\begin{equation}
\begin{split}
SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
\end{split}
\label{eq:SC_MFG_2}
\end{equation}
Repeating the calculation for $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$ (using equations (\ref{eq:eta_bar_MKV}) and (\ref{eq:x_bar_MKV})), we arrive at:
\begin{equation*}
\begin{split}
\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2 \\
&+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg],
\end{split}
\end{equation*}
Using the terminal condition for $\bar{\eta}^{MKV}_T$, equation (\ref{eq:SC_MKV_1}) can be rewritten as:
\begin{equation}
SC^{MKV} = h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2.
\label{eq:SC_MKV_2}
\end{equation}

@@

\begin{proposition}
	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by
	\begin{equation*}
		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
	\end{equation*}
\label{prop:diff_SC}
\end{proposition}
\begin{proof}
	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the Riccati equations (\ref{eq:eta_bar_MFG}) and (\ref{eq:eta_bar_MKV}), respectively, are well defined under assumption (\ref{eq:assumptions}) (see Appendix \ref{appendix_solving_fbsdes}). We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
	\begin{equation*}
		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t,
		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
	\end{equation*}
	with coefficients:
	\begin{equation*}
	\left\{
		\begin{array}{rcl}
			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\
			\beta_t &=& \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q + \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)).
		\end{array}
	\right.
	\end{equation*} 
	Since $q_T + \bar{q}_T(1-s_T) = \bar{\eta}_T^{MFG}$, $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}) that:
	\begin{equation*}
		\begin{split}
			& SC^{MFG} - SC^{MKV}\\
			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 (\mathbb{E}(\xi))^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
			=& \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2\left(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}\right) - \gamma_t\right] dt\\
			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
		\end{split}
	\end{equation*}
	where we use equation (\ref{eq:x_bar_MFG}) for the fourth equality.

@@

We study in the following the variation of $PoA$ by letting one of the coefficients tend to $0$ or to $\infty$. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right) & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1) & \qquad & 
		A^\eta &=& - b_1 \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}} \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s))& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2 & \qquad &
		C^\eta &=& q + \bar{q} \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)) & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2 & \qquad & 
		D^\eta &=& q_T + \bar{q}_T 
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{-(C^u+D^u \delta^+_u) + (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(\delta^-_u - D^u B^u) - (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. We have analogous expressions for $w_t$ and $\eta_t$ in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

@@

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this coefficient.

@@

	% modification Main point 5 (nicolas)
	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
	\begin{equation}
		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	\begin{split}
	\text{when } A^u \neq 0,\qquad & u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u},\\
	\text{when } A^u = 0, \qquad & u_t^{r \to \infty} = D^{r \to \infty}_u + C^{r \to \infty}_u (T-t).
	\end{split}
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$.

	From the formula (\ref{eq:riccati_ut}), we can bound the solution $u^r$ uniformly over $[0,T]$ for large enough $r$. More precisely, under assumption (\ref{eq:assumptions}), we have $B^r>0, C^{u,r}>0, D^{u,r}>0$, and $\delta^{+,r}_u > 0 > \delta^{-,r}_u$. In the asymptotic regime, we have $\lambda^{r\to \infty} >0$, $C^{r \to \infty}_u >0$ and $D^{r \to \infty}_u \geq 0$. Thus, for $r$ large enough, there exists a constant $\zeta > 0 $ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \zeta$. We also observe the following two inequalities when $A^u \neq 0$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert -(C^{u,r} + D^{u,r} \delta^{+,r}_u) + (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		=& C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		< & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		= & C^{u,r} + D^{u,r} 2 \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		\leq&  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( \delta^{-,r}_u - D^{u,r} B^{r} ) - (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		= & D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
		\geq & \max \left\{ - \delta^{-,r}_u , \delta_u^{+,r} e^{2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
		= & \max \left\{ A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } , (-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
		\geq & \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\}\\
		> & 0
	\end{IEEEeqnarray*}

>>>>

In the following, we intend to simplify the explicit solutions (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) for the social costs in the LQEMFG and LQEMKV problems. First, consider the quantity $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$. Using equation (\ref{eq:eta_bar_MFG}), we have:
\begin{equation*}
\begin{split}
&\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
&= - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T ((2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \right]\\
\end{split}
\end{equation*}
Then by integration by parts:
\begin{equation*}
\begin{split}
= & - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2-\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2-2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t\dot{\bar{x}}^{MFG}_t dt \\
& + \int_0^T ( (2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s)) (\bar{x}^{MFG}_t)^2 dt \Bigg] \\
\end{split}
\end{equation*}
Then using equation (\ref{eq:x_bar_MFG}):
\begin{equation*}
\begin{split}
= & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
&- \int_0^T  (\bar{b}_1 \bar{\eta}^{MFG}_t -(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
\end{split}
\end{equation*}
Finally, we solve:
\begin{equation*}
\begin{split}
\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
&+ \int_0^T  (-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
\end{split}
\end{equation*}
If we denote:
\begin{equation*}
\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},
\end{equation*}
\begin{equation*}
h_{var}: = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T,
\end{equation*}
and use the terminal condition for $\bar{\eta}^{MFG}_T$, then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
\begin{equation}
\begin{split}
SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
\end{split}
\label{eq:SC_MFG_2}
\end{equation}
Repeating the calculation for $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$ (using equations (\ref{eq:eta_bar_MKV}) and (\ref{eq:x_bar_MKV})), we arrive at:
\begin{equation*}
\begin{split}
\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2 \\
&+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg],
\end{split}
\end{equation*}
Using the terminal condition for $\bar{\eta}^{MKV}_T$, equation (\ref{eq:SC_MKV_1}) can be rewritten as:
\begin{equation}
SC^{MKV} = h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2.
\label{eq:SC_MKV_2}
\end{equation}

@@

\begin{proposition}
	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by
	\begin{equation*}
		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
	\end{equation*}
\label{prop:diff_SC}
\end{proposition}
\begin{proof}
	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the Riccati equations (\ref{eq:eta_bar_MFG}) and (\ref{eq:eta_bar_MKV}), respectively, are well defined under assumption (\ref{eq:assumptions}) (see Appendix \ref{appendix_solving_fbsdes}). We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
	\begin{equation*}
		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t,
		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
	\end{equation*}
	with coefficients:
	\begin{equation*}
	\left\{
		\begin{array}{rcl}
			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\
			\beta_t &=& \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q + \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)).
		\end{array}
	\right.
	\end{equation*} 
	Since $q_T + \bar{q}_T(1-s_T) = \bar{\eta}_T^{MFG}$, $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}) that:
	\begin{equation*}
		\begin{split}
			& SC^{MFG} - SC^{MKV}\\
			&= \frac{1}{2} \left[ \Delta\bar{\eta}_0 (\mathbb{E}(\xi))^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
			&= \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
			&= \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
			&= \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2\left(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}\right) - \gamma_t\right] dt\\
			&= \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
		\end{split}
	\end{equation*}
	where we use equation (\ref{eq:x_bar_MFG}) for the fourth equality.

@@

We study in the following the variation of $PoA$ by letting one of the coefficients tend to $0$ or to $\infty$. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right) & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1) & \qquad & 
		A^\eta &=& - b_1 \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}} \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s))& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2 & \qquad &
		C^\eta &=& q + \bar{q} \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)) & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2 & \qquad & 
		D^\eta &=& q_T + \bar{q}_T 
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{(C^u+D^u \delta^+_u) - (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(-\delta^-_u + D^u B^u) + (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. We have analogous expressions for $w_t$ and $\eta_t$ in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

@@

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

	% modification Main point 5 (nicolas)
	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
	\begin{equation}
		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	\begin{split}
	\text{when } A^u \neq 0,\qquad & u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u},\\
	\text{when } A^u = 0, \qquad & u_t^{r \to \infty} = D^{r \to \infty}_u + C^{r \to \infty}_u (T-t).
	\end{split}
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.

	Note that $B^r, C^{u,r}, \lambda^{r\to \infty}, C^{r \to \infty}_u>0$, $D^{u,r} , D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that for $r \geq r^*$, we have $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$. When $A^u \neq 0$, we have the following two inequalities for $r \geq r^*$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
		&\geq \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq  \max \left\{ - \delta^{-,r}_u , \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
		&=  \max \left\{ A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } , (-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
		&\geq  \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\}\\
		&>  0
	\end{IEEEeqnarray*}
